Galaxy Zoo: Classifications for Galaxies in HST Legacy Imaging

### 2015-08-05 writeup/gz_hubble_data.tex
mel writeup stuff, probably delete after figuring out ps vs pdf

% Journals
\newcommand{\mnras}{MNRAS}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\aj}{AJ}
\newcommand{\pasp}{PASP}
\newcommand{\aaps}{A\&AS}
\newcommand{\aap}{A\&A}
\newcommand{\apjs}{ApJS}
\newcommand{\araa}{ARA\&A}
\newcommand{\pbar}{p_{\rm bar}}
\newcommand{\fHI}{f_{\rm HI}}

@@

\usepackage{epsfig}
\begin{document}

@@

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}
\includegraphics[width=60mm]{example_ferengi2.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshirting.  \label{exampleFERENGI}}
\end{center}
\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.ps}
%\includegraphics[height=80mm,angle=-90]{TuningFork.ps}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

\includegraphics[width=0.35\textwidth,angle=90]{somewhat_fake_results.ps}

@@

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------

>>>>

% Journals
%\newcommand{\mnras}{MNRAS}
%\newcommand{\apj}{ApJ}
%\newcommand{\apjl}{ApJL}
%\newcommand{\aj}{AJ}
%\newcommand{\pasp}{PASP}
%\newcommand{\aaps}{A\&AS}
%\newcommand{\aap}{A\&A}
%\newcommand{\apjs}{ApJS}
%\newcommand{\araa}{ARA\&A}
%\newcommand{\pbar}{p_{\rm bar}}
%\newcommand{\fHI}{f_{\rm HI}}

@@

\usepackage{epsfig}
%\usepackage{epstopdf}
\begin{document}

@@

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}
\includegraphics[width=60mm]{example_ferengi2.pdf}
%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshirting.  \label{exampleFERENGI}}
\end{center}
\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

@@

\begin{figure*}
\includegraphics[width=160mm]{example_ferengi.pdf}
%\includegraphics[height=80mm,angle=-90]{TuningFork.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

\includegraphics[width=0.35\textwidth]{somewhat_fake_results.pdf}

@@

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------
\subsubsection{Results of Zeta Approach (Mel stuff)}

\begin{figure*}
\begin{center}
\includegraphics[width=8in]{p_vs_p_SB_redshift.pdf}
\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the FERENGI images relative to their lowest simulated redshift ($\rm z_{sim}=0.3$). For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$. Only images corresponding to galaxies which also had FERENGI images at $z=0.3$ were included in this plot, which include 4031 out of the total 6624.

Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value would have been if it had been viewed at $z=0.3$. This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section. We determine that a predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is one corresponding value of $p_{\rm features}$ at $z=0.3$.

In Figure \ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space. Our criteria for determining whether a region of this space is correctable is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ for fixed $p_{\rm features,z}$ in bins of $\Delta p_{\rm features,z} = 0.1$. These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin. First, we require at least 5 points in each sub-bin to determine with confidence whether that region is correctable or uncorrectable. For the region to be considered correctable, we require that the inner two quartiles of the distribution of $p_{\rm features,z=0.3}$ within these sub-bins span a range less than 0.2. These regions are coloured purple, and the inner two quartile ranges are indicated by the black error bars within each sub-bin.If the spread is greater than 0.2, the region is considered uncorrectable; these are marked in green. Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and left uncoloured on the plot.

Stuff to do in this section:

\begin{itemize}
\item talk about where purple and green tend to be on plot, and about how green areas are primarily ellipticals and disks with all the features washed out - can't tell them apart! hence, can't debias
\item talk about where the Hubble sample falls in this space, reference table \ref{hubble_debiasable} 
\item justify N>5 and spread < 0.2 (or find a better way to choose criteria)
\item check out corrections for correctable and NEI, show some sample images of corrected galaxies
\item show some data for $p_{bar}$, determine or justify why we won't debiase them  
\end{itemize}

\begin{table}
\caption{Debiasable Hubble Stuff. Doesn't include SDSS yet. Note: stuff without good redshift info automatically gets put in uncorrectable category - which is about 25,000 galaxies. Might increase correctable number if we can get these measurements. \label{hubble_debiasable}}
\begin{tabular}{lrr}
\hline\hline
Category &  N & \% \\
\hline
Correctable   & 7408 & 6 \%  \\
Uncorrectable & 58526 & 50 \%\\
NEI           & 52149 & 44 \% \\
Total         & 118083 & 100 \% \\
\hline\hline
\end{tabular}
\end{table}
